---
title: "FVS Percent Change"
author: "Anna Talucci"
date: "1/27/2024"
output: html_document
---
# Overview
Create bar plot to showing percent change at year 20 compared to baseline across the 108 scenarios for Total Stand Carbon. 

## Set global options
Prevent scientific notation of numeric values; use =0 to reset
```{r}
options(scipen=999)
```

# Library
```{r}
library(tidyverse)
library(cowplot)
```

# Data
Read in FVS HUC12 level data.
```{r}
fvs = read_csv("../data/FVS/FVSprocessedOutputsHucs.csv")
```
```{r}
fvs
```

```{r}
( TSCScenario = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarize(meanTSC = mean(TSC),
            meanQMD = mean(QMD),
            meanSDI = mean(SDI), 
            meanFlt3 = mean(Fuel_lt3),
            meanF3to6 = mean(Fuel_3to6),
            meanF6to12 = mean(Fuel_6to12)) %>%
  filter(Year==2024) %>%
    filter(RRK=="SC")
)
```

```{r}
sc_tsc = ggplot(TSCScenario, aes(TxIntensity, meanTSC)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean TSC") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_qmd = ggplot(TSCScenario, aes(TxIntensity, meanQMD)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean QMD") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_sdi = ggplot(TSCScenario, aes(TxIntensity, meanSDI)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean SDI") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_flt3 = ggplot(TSCScenario, aes(TxIntensity, meanFlt3)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean Fuel lt 3") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_f3to6 = ggplot(TSCScenario, aes(TxIntensity, meanF3to6)) +
  geom_bar(stat = "identity", aes(legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean Fuel 3 to 6") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```


```{r}
sc_f6to12 = ggplot(TSCScenario, aes(TxIntensity, meanF6to12)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean Fuel 6 to 12") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
grid_sc = cowplot::plot_grid(sc_tsc, sc_qmd, sc_sdi, sc_flt3, sc_f3to6, sc_f6to12)
```
```{r}
ggsave("../figures/FVS_SC_Baseline.png", plot = grid_sc, width = 10, height = 10, units = c("in"), dpi = 600)
```
## Calculate Percent Change for TSC
Select columns of interest to calculate change for each year compared to baseline (year=2024) for total stand carbon (TSC)
```{r}
TscChange = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, TSC) %>%
  pivot_wider(names_from = Year, values_from = TSC, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100) 
```
```{r}
TscChange
```

## Filter and summaries to 108 scenarios
Summaries for for 108 scenarios for total stand carbon. Add a factor variable for graphing that combines the priority and treatment type. 
```{r}
( TscPrctChnge_108 = TscChange %>% 
  group_by(RRK, Priority, TxIntensity, TxType) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>% 
      mutate(IntenseType = paste(TxIntensity,"-", TxType))%>%
    mutate(IntenseType  = factor(IntenseType , levels = c("500k - trt1", "1m - trt1", "2m - trt1", "500k - trt4", "1m - trt4", "2m - trt4", "500k - trt6",   "1m - trt6",  "2m - trt6")))
)
```

## Bar Plot
```{r fig.height=10, fig.width=10}
( tsc_plot = ggplot(TscPrctChnge_108, aes(IntenseType, prct2044_mean)) +
  geom_bar(stat = "identity", aes(fill = IntenseType, legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Percent Change at 20 years for Total Stored Carbon") +
  facet_wrap(~RRK + Priority,  ncol = 3 ) +
  scale_fill_manual(values=c('#d53e4f','#f46d43','#fdae61','#fee08b','#ffffbf','#e6f598','#abdda4','#66c2a5','#3288bd')) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Priority & treatment type") +
  theme(legend.position = "none") 
)
```

### Save as png
```{r}
ggsave("../figures/TSCchangeBarPlot.png", plot = tsc_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```

