---
title: "FVS Summary"
author: "Anna Talucci"
date: "3/21/2024"
output: html_document
---
```{r clearEnvironment, include=FALSE}
rm(list=ls())
```

```{r globalOptions, include=FALSE}
options(scipen=999) #Prevent scientific notation of numeric values; use =0 to reset
```

# Overview

HUC Treatment timing


Sample HUCS for graphing

HUC12	Region	group	priority
180701020701	SC	50	fire
180702030506	SC	50	fire
180703020504	SC	75	fire
180701010104	SC	75	fire
181002041506	SC	50	wui
180703010402	SC	50	wui
180703030103	SC	75	wui
180600140201	SC	75	wui
181002030401	SC	50	hybrid
180703030502	SC	50	hybrid
180703030101	SC	75	hybrid
180600130106	SC	75	hybrid
180701020106	SC	25	fire
180701020303	SC	25	fire
181002010703	SC	100	fire
181002020304	SC	100	fire
180702020303	SC	25	wui
180701030104	SC	25	wui
180703020301	SC	100	wui
180300031401	SC	100	wui
180701020107	SC	25	hybrid
180702030605	SC	25	hybrid
180703010403	SC	100	hybrid
181002030501	SC	100	hybrid

# Packages

```{r}
library(tidyverse)
library(sf)
library(RColorBrewer)
library(scales)
library(ggnewscale)
library(cowplot)
```


# Data

```{r}
vegtype = read.csv("../data/vegType/AllHucsHerbShrubHardSoft.csv")
```

```{r}
fvs = read_csv("../data/FVS/FVSprocessedOutputsHucsScCcSn.csv")
```
```{r}
fvs
```

```{r}
unique(fvs$Priority)
```
```{r}
( timingGroups = fvs %>% dplyr::select(huc12, region, regionName, timeWui, timeFire, timeHybrid) )
```
# Veg type proportion by HUC
```{r}
(vegtype = allHucs %>% 
   dplyr::select(huc12, RRK_Region, hardwoodSum, 
herbSum, shrubSum, softwoodSum, vegSum) %>%
  mutate(Herb = herbSum/vegSum,
         Shrub = shrubSum/vegSum,
         Hardwood = hardwoodSum/vegSum,
         Softwood = softwoodSum/vegSum) %>%
  dplyr::select(huc12, RRK_Region, Herb:Softwood) %>%
  rename(regionName=RRK_Region) %>%
  pivot_longer(!c(huc12, regionName), names_to = "vegType", values_to = "Proportion")

)
```

## add timing
```{r}
( vegtype1 = full_join(vegtype, timingGroups, by=c("huc12", "regionName") ) )
```

# Fire 
```{r}
targetFire = c('180701020701',
'180702030506',	
'180703020504',	
'180701010104',
'180701020106',	
'180701020303',	
'181002010703',	
'181002020304')
```

```{r}
(fireHucs = fvs %>% 
   filter(huc12 %in% targetFire) %>% 
   filter(Priority=="Fire") %>% 
   mutate(timeFire = fct_relevel(timeFire, "yr1to5", "yr6to10", "yr11to15", "yr16to20")) %>%
   mutate(Intensity = fct_relevel(Intensity, "500k", "1m", "2m"))

)
```

# Plot Fire priority TSC
['#ffffb2','#fecc5c','#fd8d3c','#f03b20','#bd0026']
```{r}
( timeseriesSCFire = fireHucs %>% 
  group_by(Intensity, TxType) %>%
  ggplot(., aes(x=Year, y=TSC, group=as.character(huc12), color=timeFire)) +
  geom_point() + 
  geom_line() + 
  facet_grid(TxType ~ Intensity) +
  scale_color_manual( values = c('#bd0026', '#f03b20','#fd8d3c','#fecc5c'), name="Tx timing") +
  theme_bw()  #+
#guides(color=guide_legend(title="Tx year 1-5"))
)
```
#### save tx timing
```{r}
ggsave("../figures/scFireTxTiming.png", plot=timeseriesSCFire, dpi=600, bg="white")
```

## Veg bar plot
```{r}

(vegtypefireHucs = vegtype1 %>% 
   filter(huc12 %in% targetFire) %>% 
   mutate(timeFire = fct_relevel(timeFire, "yr1to5", "yr6to10", "yr11to15", "yr16to20")) %>%
   distinct(.keep_all = TRUE) %>%
   mutate(x = paste(huc12, " ", timeFire)) 

)

```

````{r}
( scFireHucs = ggplot(vegtypefireHucs, aes(x=vegType, y=Proportion)) +
    geom_bar(stat="identity") +
    facet_wrap(~x, ncol=2) +
    theme_bw() +
    labs(x="")
)
```
#### save veg bar plot
```{r}
ggsave("../figures/scFireHucsPropVegType.png", plot=scFireHucs, width = 5, height = 6, units = "in", dpi=600, bg="white")
```