---
title: "FVS Summary Plots"
author: "Anna Talucci"
date: "1/25/2024"
output: html_document
---

```{r clearEnvironment, include=FALSE}
rm(list=ls())
```

```{r globalOptions, include=FALSE}
options(scipen=999) #Prevent scientific notation of numeric values; use =0 to reset
```

# Overview
**NEEDS UPDATING**

Create scatter plots with join distribution of 500k (x-axis) versus 2.3 million (y-axis) intensity. 


# Library
```{r}
library(tidyverse)
```

# Data
Read in FVS huc level data.

```{r}
fvs = read_csv("../data/FVS/FVSprocessedOutputsHucsScCcSnBase.csv")
```

```{r}
fvs
```

# Reorganization data for joint distribution plots
Check unique codes for treatment intensity
```{r}
unique(fvs$Intensity)

```

## Filter for 500k intensity
```{r}
TxI500k = fvs %>% 
  filter(Intensity == "500k") %>% 
  filter(Year==2039) %>%
  rename(TSC500k=TSC, SDI500k=SDI, QMD500k=QMD, Fuel_lt3500k = Fuel_lt3, Fuel_3to6500k=Fuel_3to6, Fuel_6to12500k=Fuel_6to12)
```

## Filter for 500k intensity
```{r}
TxI500 = fvs %>% 
  filter(Intensity == "500k") %>% 
  filter(Year==2039) %>%
  rename(TSC500k=TSC, SDI500k=SDI, QMD500k=QMD, Fuel_lt3500k = Fuel_lt3, Fuel_3to6500k=Fuel_3to6, Fuel_6to12500k=Fuel_6to12)
```

## Filter for 2.3 million intensity
```{r}
TxI2m = fvs %>% 
  filter(Intensity == "2m") %>% 
  filter(Year==2039) %>%
  rename(TSC2m=TSC, SDI2m=SDI, QMD2m=QMD, Fuel_lt32m = Fuel_lt3, Fuel_3to62m=Fuel_3to6, Fuel_6to122m=Fuel_6to12)
```

## Join new data frames
```{r}
df1 = cbind(TxI500, TxI2m) 
glimpse(df1)
```

## Select variables of interest for plots
```{r}
tsc_cc = df1 %>% dplyr::select(huc12:TxType, TSC500k, TSC2m) %>% filter(region == "CC")
tsc_sc = df1 %>% dplyr::select(huc12:TxType, TSC500k, TSC2m) %>% filter(region == "SC")

```

```{r}
flt3_cc = df1 %>% dplyr::select(huc12:TxType, Fuel_lt3500k, Fuel_lt32m) %>% filter(region == "CC")
flt3_sc = df1 %>% dplyr::select(huc12:TxType, Fuel_lt3500k, Fuel_lt32m) %>% filter(region == "SC")
```

# Joint Distribution Visualizations

## Total Stand Carbon
```{r fig.height=10, fig.width=10}
(
  tsc_plot_cc = ggplot(data = tsc_cc, aes(x=TSC500k, y=TSC2m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Total Stand Carbon (mt/ac)", y= "2m Total Stand Carbon (mt/ac) ")
)
```

### Save 
```{r}
ggsave("../figures/TSC2039_500kv2m_CC.png", plot = tsc_plot_cc, width = 10, height = 10, units = c("in"), dpi = 600)
```

```{r fig.height=10, fig.width=10}
(
  tsc_plot_sc = ggplot(data = tsc_sc, aes(x=TSC500k, y=TSC2m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Total Stand Carbon (mt/ac)", y= "2m Total Stand Carbon (mt/ac) ")
)
```

### Save 
```{r}
ggsave("../figures/TSC2039_500kv2m_SC.png", plot = tsc_plot_sc, width = 10, height = 10, units = c("in"), dpi = 600)
```


## Fuel Load less than 3" diameter CC
```{r fig.height=10, fig.width=10}
(
  flt3_plot_cc = ggplot(data = flt3_cc, aes(x=Fuel_lt3500k, y=Fuel_lt32m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Fuel loads <3” diameter (mt/ac)", y= "2m Fuel loads <3” diameter (mt/ac)")
)
```

### Save
```{r}
ggsave("../figures/Flt3_2039_500kv2m_CC.png", plot = flt3_plot_cc, width = 10, height = 10, units = c("in"), dpi = 600)
```

## Fuel Load less than 3" diameter SC
```{r fig.height=10, fig.width=10}
(
  flt3_plot_sc = ggplot(data = flt3_sc, aes(x=Fuel_lt3500k, y=Fuel_lt32m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Fuel loads <3” diameter (mt/ac)", y= "2m Fuel loads <3” diameter (mt/ac)")
)
```

### Save
```{r}
ggsave("../figures/Flt3_2039_500kv2m_SC.png", plot = flt3_plot_sc, width = 10, height = 10, units = c("in"), dpi = 600)
```

