---
title: "FVS Summary Plots"
author: "Anna Talucci"
date: "1/25/2024"
output: html_document
---

```{r clearEnvironment, include=FALSE}
rm(list=ls())
```

```{r globalOptions, include=FALSE}
options(scipen=999) #Prevent scientific notation of numeric values; use =0 to reset
```

# Overview
Create scatter plots with join distribution of 500k (x-axis) versus 2.3 million (y-axis) intensity. 


# Library
```{r}
library(tidyverse)
```

# Data
Read in FVS huc level data.
```{r}
fvs = read_csv("../data/FVS/FVSprocessedOutputsHucs.csv")
```

```{r}
fvs
```

# Reorganization data for joint distribution plots
Check unique codes for treatment intensity
```{r}
unique(fvs$TxIntensity)

```

## Filter for 500k intensity
```{r}
TxI500 = fvs %>% 
  filter(TxIntensity == "500k") %>% 
  filter(Year==2044) %>%
  rename(TSC500k=TSC, SDI500k=SDI, QMD500k=QMD, Fuel_lt3500k = Fuel_lt3, Fuel_3to6500k=Fuel_3to6, Fuel_6to12500k=Fuel_6to12)
```

## Filter for 2.3 million intensity
```{r}
TxI2m = fvs %>% 
  filter(TxIntensity == "2m") %>% 
  filter(Year==2044) %>%
  rename(TSC2m=TSC, SDI2m=SDI, QMD2m=QMD, Fuel_lt32m = Fuel_lt3, Fuel_3to62m=Fuel_3to6, Fuel_6to122m=Fuel_6to12)
```

## Join new data frames
```{r}
df1 = cbind(TxI500, TxI2m) 
glimpse(df1)
```

## Select variables of interest for plots
```{r}
tsc = df1 %>% dplyr::select(HUC12:TxType, TSC500k, TSC2m)
sdi = df1 %>% dplyr::select(HUC12:TxType, SDI500k, SDI2m)
qmd = df1 %>% dplyr::select(HUC12:TxType, QMD500k, QMD2m)

flt3 = df1 %>% dplyr::select(HUC12:TxType, Fuel_lt3500k, Fuel_lt32m)
f3to6 = df1 %>% dplyr::select(HUC12:TxType, Fuel_3to6500k, Fuel_3to62m)
f6to12 = df1 %>% dplyr::select(HUC12:TxType, Fuel_6to12500k, Fuel_6to122m)
```

# Joint Distribution Visualizations

## Total Stand Carbon
```{r fig.height=10, fig.width=10}
(
  tsc_plot = ggplot(data = tsc, aes(x=TSC500k, y=TSC2m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Total Stand Carbon (mt/ac)", y= "2m Total Stand Carbon (mt/ac) ")
)
```

### Save 
```{r}
ggsave("../figures/TSC20yr500kv2m.png", plot = tsc_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```

## Stand Density Index
```{r fig.height=10, fig.width=10}
(
  sdi_plot = ggplot(data = sdi, aes(x=SDI500k, y=SDI2m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Stand density index (trees/ac)", y= "2m Stand density index (trees/ac)")
)
```

### Save
```{r}
ggsave("../figures/SDI20yr500kv2m.png", plot = sdi_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```

## Quadartic Mean Diameter
```{r fig.height=10, fig.width=10}
(
  qmd_plot = ggplot(data = qmd, aes(x=QMD500k, y=QMD2m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Quadratic mean diameter (in)", y= "2m Quadratic mean diameter (in)")
)
```

### Save
```{r}
ggsave("../figures/QMD20yr500kv2m.png", plot = qmd_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```

## Fuel Load less than 3" diameter
```{r fig.height=10, fig.width=10}
(
  flt3_plot = ggplot(data = flt3, aes(x=Fuel_lt3500k, y=Fuel_lt32m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Fuel loads <3” diameter (mt/ac)", y= "2m Fuel loads <3” diameter (mt/ac)")
)
```

### Save
```{r}
ggsave("../figures/Flt320yr500kv2m.png", plot = flt3_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```


## Fuel Load 3-6" diameter
```{r fig.height=10, fig.width=10}
( 
  f3to6_plot = ggplot(data = f3to6, aes(x=Fuel_3to6500k, y=Fuel_3to62m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Fuel loads 3-6” diameter (mt/ac)", y= "2m Fuel loads 3-6” diameter (mt/ac)")
)
```

### Save
```{r}
ggsave("../figures/F3to6at20yr500kv2m.png", plot = f3to6_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```

## Fuel Load 6-12" diameter
```{r fig.height=10, fig.width=10}
( 
  f6to12_plot = ggplot(data = f6to12, aes(x=Fuel_6to12500k, y=Fuel_6to122m)) +
    geom_point(color="grey50", alpha=.5, size=.5, shape=21) +
    facet_wrap(~Priority + TxType) +
    geom_abline(intercept = 0, slope=1) +
    theme_bw() +
    theme(aspect.ratio=1) +
    
    stat_smooth(method=lm, formula= (y ~ x), fullrange=TRUE) +
    labs(x="500k Fuel loads 6-12” diameter (mt/ac)", y= "2m Fuel loads 6-12” diameter (mt/ac)")
)
```

### Save
```{r}
ggsave("../figures/F6to12at20yr500kv2m.png", plot = f6to12_plot, width = 10, height = 10, units = c("in"), dpi = 600)
```



