---
title: "FVS Percent Change"
author: "Anna Talucci"
date: "1/27/2024"
output: html_document
---

```{r clearEnvironment, include=FALSE}
rm(list=ls())
```

```{r globalOptions, include=FALSE}
options(scipen=999) #Prevent scientific notation of numeric values; use =0 to reset
```

# Overview
**NEEDS UPDATING**
Create bar plot to showing percent change at year 20 compared to baseline across the 108 scenarios for Total Stand Carbon. 


# Library
```{r}
library(tidyverse)
library(cowplot)
```

# Data
Read in FVS HUC12 level data.


```{r}
fvs = read_csv("../data/FVS/FVSprocessedOutputsHucsScCcSnBase.csv")
```
```{r}
fvs
```

```{r}
( TSCScenario = fvs %>% 
  group_by(region, Priority, Intensity, TxType, Year) %>%
  summarize(meanTSC = mean(TSC),
            meanQMD = mean(QMD),
            meanSDI = mean(SDI), 
            meanFlt3 = mean(Fuel_lt3),
            meanF3to6 = mean(Fuel_3to6),
            meanF6to12 = mean(Fuel_6to12)) %>%
  #filter(Year==2024) %>%
    filter(region=="SC") %>%
    filter(Priority!="baseline")
)
```

```{r}
( sc_tsc = ggplot(TSCScenario, aes(Intensity, meanTSC)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean TSC") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") )
```

```{r}
sc_qmd = ggplot(TSCScenario, aes(Intensity, meanQMD)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean QMD") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_sdi = ggplot(TSCScenario, aes(Intensity, meanSDI)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean SDI") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_flt3 = ggplot(TSCScenario, aes(Intensity, meanFlt3)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean Fuel lt 3") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
sc_f3to6 = ggplot(TSCScenario, aes(Intensity, meanF3to6)) +
  geom_bar(stat = "identity", aes(legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean Fuel 3 to 6") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```


```{r}
sc_f6to12 = ggplot(TSCScenario, aes(Intensity, meanF6to12)) +
  geom_bar(stat = "identity", aes( legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Mean Fuel 6 to 12") +
  facet_wrap(~Priority + TxType,  ncol = 3 ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Intensity") +
  theme(legend.position = "none") 
```

```{r}
grid_sc = cowplot::plot_grid(sc_tsc, sc_qmd, sc_sdi, sc_flt3, sc_f3to6, sc_f6to12)
```
```{r}
ggsave("../figures/FVS_SC_Baseline.png", plot = grid_sc, width = 10, height = 10, units = c("in"), dpi = 600)
```
## Calculate Percent Change for TSC
Select columns of interest to calculate change for each year compared to baseline (year=2024) for total stand carbon (TSC)
```{r}
( TscBase = fvs %>% 
  dplyr::select(huc12,run, region, Priority, Intensity, TxType, Year, TSC) %>%
  pivot_wider(names_from = Year, values_from = TSC, names_glue = "base_{Year}") %>%
    filter(Priority=="baseline") %>%
    dplyr::select(huc12, region, base_2024, base_2029, base_2034, base_2039) 
  
)
 
( TscTxYr = fvs %>% 
  dplyr::select(huc12,run, region, Priority, Intensity, TxType, Year, TSC) %>%
  pivot_wider(names_from = Year, values_from = TSC, names_glue = "yr_{Year}") %>%
    filter(Priority!="baseline")
  
) 
```

```{r}
( tscJoin = TscTxYr %>% 
    full_join(., TscBase, by=c('huc12', 'region')) 
)
```

```{r}
( tscChange = tscJoin %>% 
  mutate(diff2024 = yr_2024-base_2024,
         diff2029 = yr_2029-base_2029,
         diff2034 = yr_2034-base_2034,
         diff2039 = yr_2039-base_2039,
         prct2024 = (diff2024/base_2024)*100,
         prct2029 = (diff2029/base_2029)*100,
         prct2034 = (diff2034/base_2034)*100,
         prct2039 = (diff2039/base_2039)*100) 
)

```


```{r}
tscChange
```

## Filter and summaries to 108 scenarios
Summaries for for 108 scenarios for total stand carbon. Add a factor variable for graphing that combines the priority and treatment type. 
```{r}
( TscPrctChnge_CcSc = tscChange %>% 
  group_by(region, Priority, Intensity, TxType) %>%
  summarise_at(vars('prct2024','prct2029', 'prct2034', 'prct2039'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>% 
     mutate(IntenseType = paste(Intensity,"-", TxType))%>%
    mutate(IntenseType  = factor(IntenseType , levels = c("500k - trt1", "1m - trt1", "2m - trt1", "500k - trt4", "1m - trt4", "2m - trt4", "500k - trt6",   "1m - trt6",  "2m - trt6"))) %>% 
    filter(region %in% c("CC", "SC"))
) 
```

## Bar Plot
```{r fig.height=10, fig.width=10}
( tsc_plotCcSc = ggplot(TscPrctChnge_CcSc, aes(IntenseType, prct2039_mean)) +
  geom_bar(stat = "identity", aes(fill = IntenseType, legend = FALSE)) + 
  #geom_text(aes(label = paste(round(prct2044_mean, 1), "%"),
              # vjust = ifelse(prct2044_mean >= 0, 0, 1))) +
  scale_y_continuous("Percent Change at 20 years for Total Stored Carbon") +
  facet_wrap(~region + Priority,  ncol = 3 ) +
  scale_fill_manual(values=c('#d53e4f','#f46d43','#fdae61','#fee08b','#ffffbf','#e6f598','#abdda4','#66c2a5','#3288bd')) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x="Priority & treatment type") +
  theme(legend.position = "none") 
)
```

### Save as png
```{r}
ggsave("../figures/TSCchangeBarPlotCcSc.png", plot = tsc_plotCcSc, dpi = 600)
```

