---
title: "Redo ranks by WIP for SN"
output: html_document
---

# Overview
Calculate check for min max of percent rank, error in calculation

Note: found error in EE code and fixed.


# Packages
```{r}
library(tidyverse)
library(skimr)
```

# Data

## Shapefile
```{r}
hucs = st_read("../data/SelectedHucs/HucsRrkWip.shp", "HucsRrkWip")
```

## CSV from EE
```{r}
sn = read.csv("../data/RrkCsv/snHucTreat10WuiBpPrctRk_2023-05-07.csv")
```

## CSV from EE
```{r}
cc = read.csv("../data/RrkCsv/ccHucTreat10WuiBpPrctRk_2023-05-07.csv")
nc = read.csv("../data/RrkCsv/ncHucTreat10WuiBpPrctRk_2023-05-07.csv")
sc = read.csv("../data/RrkCsv/scHucTreat10WuiBpPrctRk_2023-05-07.csv")
```

# Look at data
```{r}
glimpse(sn)
```

```{r}
glimpse(cc)
glimpse(nc)
glimpse(sc)
```


```{r}
skimr::skim(sn)
```

```{r}
sn
```
# Update Ranks

## Scale funtion
To rescale and start at 1 instead of zero
```{r}
scale_rank = function(x) (x+1)
```

## Rescale Within RRK
```{r}
(
  sn1 = sn %>% 
    dplyr::select(Acres, BpMean:RRK_Region, WIPGeoNam:areasqkm, huc12:hutype, name, states:sumsqkm) %>%
    mutate(across(c(BpMean, BpPrct, PropTreat, PropWui, WuiPrct, sum, sumsqkm), round, 3)) %>%
    mutate(across(c(BpRank, WuiRank), scale_rank)) %>%
    mutate(BpPrct = round(BpRank/n() *100, 2)) %>%
    mutate(WuiPrct = round(WuiRank/n() *100, 2))
)
```

```{r}
(
  cc1 = cc %>% 
    dplyr::select(Acres, BpMean:RRK_Region, WIPGeoNam:areasqkm, huc12:hutype, name, states:sumsqkm) %>%
    mutate(across(c(BpMean, BpPrct, PropTreat, PropWui, WuiPrct, sum, sumsqkm), round, 3)) %>%
    mutate(across(c(BpRank, WuiRank), scale_rank)) %>%
    mutate(BpPrct = round(BpRank/n() *100, 2)) %>%
    mutate(WuiPrct = round(WuiRank/n() *100, 2))
)
```


```{r}
(
  nc1 = nc %>% 
    dplyr::select(Acres, BpMean:RRK_Region, WIPGeoNam:areasqkm, huc12:hutype, name, states:sumsqkm) %>%
    mutate(across(c(BpMean, BpPrct, PropTreat, PropWui, WuiPrct, sum, sumsqkm), round, 3)) %>%
    mutate(across(c(BpRank, WuiRank), scale_rank)) %>%
    mutate(BpPrct = round(BpRank/n() *100, 2)) %>%
    mutate(WuiPrct = round(WuiRank/n() *100, 2))
)
```

```{r}
(
  sc1 = sc %>% 
    dplyr::select(Acres, BpMean:RRK_Region, WIPGeoNam:areasqkm, huc12:hutype, name, states:sumsqkm) %>%
    mutate(across(c(BpMean, BpPrct, PropTreat, PropWui, WuiPrct, sum, sumsqkm), round, 3)) %>%
    mutate(across(c(BpRank, WuiRank), scale_rank)) %>%
    mutate(BpPrct = round(BpRank/n() *100, 2)) %>%
    mutate(WuiPrct = round(WuiRank/n() *100, 2))
)
```

# Rank within WIPs
```{r}
( 
  wipRanks = rank1 %>% 
    arrange(BpRank) %>%
    group_by(WIPGeoNam) %>%
    mutate(BpRankWip = rank(BpRank)) %>%
    ungroup() %>%
    arrange(WuiRank) %>%
    group_by(WIPGeoNam) %>%
    mutate(WuiRankWip = rank(WuiRank))
)
  
```
```{r}
wipRanks %>%
    group_by(WIPGeoNam) %>%
  dplyr::tally()
```
mutate(WipGroupSize = ifelse(WIPGeoNam == "East Side", 181,
                          ifelse(WIPGeoNam == "Eldorado South", 178,
                          ifelse(WIPGeoNam == "North East", 120,
                          ifelse(WIPGeoNam == "North West - Pit", 140,
                          ifelse(WIPGeoNam == "Sacramento - Feather", 185,
                          ifelse(WIPGeoNam == "Southern", 255,
                          ifelse(WIPGeoNam == "TCSI Plus", 130,26)))))))) 
                          
```{r}
(
  wipRanks1 = wipRanks %>%
    group_by(WIPGeoNam) %>%
    mutate(BpPrctWip = round(BpRankWip/n() *100, 2)) %>%
    mutate(WuiPrctWip = round(WuiRankWip/n() *100, 2)) 
)
```

```{r}
(
  check = wipRanks1 %>%
    group_by(WIPGeoNam) %>%
    summarize(minBpPrctWip = min(BpPrctWip),
            maxBpPrctWip = max(BpPrctWip),
            minWuiPrctWip = min(WuiPrctWip),
            maxWuiPrctWip = max(WuiPrctWip))
)

```

# Select Shape file
```{r}
( sn_rrk = hucs %>% filter (RRK_Region =="Sierra Nevada Region") %>% dplyr::select(huc12))
( cc_rrk = hucs %>% filter (RRK_Region =="Central Coast Region") %>% dplyr::select(huc12))
( nc_rrk = hucs %>% filter (RRK_Region =="North Coast Region") %>% dplyr::select(huc12))
( sc_rrk = hucs %>% filter (RRK_Region =="Sout Coast Region") %>% dplyr::select(huc12))
```

# join
```{r}
( snPrctRank = merge(x = sn_rrk, y = wipRanks1, by = "huc12", all = TRUE) )
```

```{r}
( ccPrctRank = merge(x = cc_rrk, y = cc1, by = "huc12", all = TRUE) )
```

```{r}
( ncPrctRank = merge(x = nc_rrk, y = nc1, by = "huc12", all = TRUE) )
```

```{r}
( scPrctRank = merge(x = sc_rrk, y = sc1, by = "huc12", all = TRUE) )
```
# Head data frame
```{r}
glimpse(ccPrctRank)
glimpse(ncPrctRank)
glimpse(scPrctRank)
glimpse(snPrctRank)
```
```{r}
scPrctRank = scPrctRank %>% mutate(huc12 = as.character(huc12))
```
# Bind rows into one shapefile

```{r}
( allData = bind_rows(ccPrctRank, ncPrctRank, scPrctRank, snPrctRank) )
```


# Write to shp
```{r}
st_write(snPrctRank, "../outputs/snPrctRankWIP.shp", driver="ESRI Shapefile")
```
```{r}
st_write(allData, "../outputs/allHucsPrctRankWIP.shp", driver="ESRI Shapefile")
```