---
title: "Summarize Fvs"
author: "Anna Talucci"
date: "12/19/2023"
output: html_document
---

---
title: "Summary FVS Processed Outputs"
author: "Anna Talucci"
date: "12/2/2023"
output: html_document
---



# Overview
Summary table for FVS Processed outputs by RRK

# Global options
prevent scientific notation; use =0 to reset
```{r}
options(scipen=999)
```

# Library
```{r}
library(tidyverse)

library(vroom)

```


# Data

```{r}
fvs = read_csv("../data/FVS/FVSprocessedOutputsHucs.csv")
```

```{r}
fvs
```

# Investigate SC Zero Issue
```{r}
(scZero = fvs %>% filter(RRK=="SC") %>% filter(TSC==0) )

cat(paste0(sprintf('%s', unique(scZero$HUC12)), collapse = ", "))

```
# Basic Summary Stats
```{r}
fvs
```

```{r}
TSCSummary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarise_at("TSC", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsTscSummary432.csv", row.names = F)
```

 %>%
  write.csv(., "../outputs/fvs/FvsTscSummary.csv", row.names = F)
```{r}
SDISummary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarise_at("SDI", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsSdiSummary432.csv", row.names = F)
```

```{r}
QMDSummary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarise_at("QMD", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsQmdSummary432.csv", row.names = F)
```

```{r}
Flt3Summary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarise_at("Fuel_lt3", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsFlt3Summary432.csv", row.names = F)
```

```{r}
F3t6Summary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarise_at("Fuel_3to6", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsF3t6Summary432.csv", row.names = F)
```

```{r}
F6t12Summary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, Year) %>%
  summarise_at("Fuel_6to12", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsF6t12Summary432.csv", row.names = F)
```

# Summary by Run & Treatment 108
```{r}
TSCSummary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, run) %>%
  summarise_at("TSC", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsTscSummary108.csv", row.names = F)
```

 %>%
  write.csv(., "../outputs/fvs/FvsTscSummary.csv", row.names = F)
```{r}
SDISummary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, run) %>%
  summarise_at("SDI", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsSdiSummary108.csv", row.names = F)
```

```{r}
QMDSummary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, run) %>%
  summarise_at("QMD", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsQmdSummary108.csv", row.names = F)
```

```{r}
Flt3Summary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, run) %>%
  summarise_at("Fuel_lt3", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsFlt3Summary108.csv", row.names = F)
```

```{r}
F3t6Summary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, run) %>%
  summarise_at("Fuel_3to6", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsF3t6Summary108.csv", row.names = F)
```

```{r}
F6t12Summary = fvs %>% 
  group_by(RRK, Priority, TxIntensity, TxType, run) %>%
  summarise_at("Fuel_6to12", .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/FvsF6t12Summary108.csv", row.names = F)
```

# Calculate Difference from Baseline

```{r}
fvs
```

## TSC
```{r}
TscChange = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, TSC) %>%
  pivot_wider(names_from = Year, values_from = TSC, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100)
```

## SDI
```{r}
SdiChange = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, SDI_x_100) %>%
  pivot_wider(names_from = Year, values_from = SDI_x_100, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100)
```

((yr_2029-yr_2024)/yr_2024*100))
## QMD
```{r}
QmdChange = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, QMD_x_100) %>%
  pivot_wider(names_from = Year, values_from = QMD_x_100, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100)
```

## Fuellt3
```{r}
Flt3Change = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, Fuel_lt3_x_100) %>%
  pivot_wider(names_from = Year, values_from = Fuel_lt3_x_100, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100)
```

## Fuel_3to6
```{r}
F3to6Change = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, Fuel_3to6_x_100) %>%
  pivot_wider(names_from = Year, values_from = Fuel_3to6_x_100, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100)
```

### zero issue
```{r}
F3to6Change %>% 
  filter(RRK=="SC") %>% 
  filter(yr_2044==0) %>%
  write.csv(., "../outputs/fvs/SC_Zero_Issue.csv", row.names = F)
```
```{r}
zeroF3to6Change = F3to6Change %>% 
  filter(RRK=="SC") %>% 
  filter(yr_2044==0) 
```
```{r}
fvs %>% 
  filter(RRK=="SC") %>% 
  select(HUC12, Year, Fuel_3to6_x_100, Fuel_6to12_x_100) %>% 
  group_by(HUC12) %>% right_join(zeroF3to6Change, by='HUC12')
```

```{r}
fvs %>% 
  filter(RRK=="SC") %>%
  group_by(HUC12) %>% 
  filter(Fuel_3to6_x_100==0 | Fuel_6to12_x_100==0) %>% 
  write.csv(., "../outputs/fvs/SCZeroIssueProcessed.csv", row.names = F)
```
```{r}
zeroF3to6Change = F3to6Change %>% 
  filter(RRK=="SC") %>% 
  filter(yr_2044==0) 
```

```{r}
( 
  zeroSc = fvs %>% 
  filter(RRK=="SC") %>% 
  select(HUC12, Year, Fuel_3to6_x_100, Fuel_6to12_x_100) %>% 
  group_by(HUC12) %>% 
  filter( Fuel_6to12_x_100==0) 
)

```

```{r}
unique(zeroSc$HUC12)
```

## Fuel_6to12
```{r}
F6to12Change = fvs %>% 
  dplyr::select(HUC12,run, RRK, Priority, TxIntensity, TxType, Year, Fuel_6to12_x_100) %>%
  pivot_wider(names_from = Year, values_from = Fuel_6to12_x_100, names_glue = "yr_{Year}") %>%
  mutate(baseline = yr_2024,
         diff2029 = yr_2029-yr_2024,
         diff2034 = yr_2034-yr_2024,
         diff2044 = yr_2044-yr_2024,
         prct2029 = (diff2029/baseline)*100,
         prct2034 = (diff2034/baseline)*100,
         prct2044 = (diff2044/baseline)*100)
```


# Summaries for Change

## TSC
```{r}
TscPrctChnge = TscChange %>% 
  group_by(RRK) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/TscPrctChng.csv", row.names = F)
```

## SDI
```{r}
sdiPrctChng = SdiChange %>% 
  group_by(RRK) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/SdiPrctChng.csv", row.names = F)
```

## QMD
```{r}
QMDPrctChng = QmdChange %>% 
  group_by(RRK) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/QmdPrctChng.csv", row.names = F)
```

## Fuellt3
```{r}
Flt3PrctChng = Flt3Change %>% 
  group_by(RRK) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/Flt3PrctChng.csv", row.names = F)
```

## Fuel 3 to 6
```{r}
F3t6PrctChng = F3to6Change %>% 
  group_by(RRK) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/F3t6PrctChng.csv", row.names = F)
```

## Fuel 6 to 12
```{r}
F6t12PrctChng = F6to12Change %>% 
  group_by(RRK) %>%
  summarise_at(vars('prct2029', 'prct2034', 'prct2044'), .funs = lst(mean, sd, median, min, max), na.rm = TRUE) %>%
  write.csv(., "../outputs/fvs/F6t12PrctChng.csv", row.names = F)
```



