---
title: "Summarize Treatment Runs"
author: "Anna Talucci"
date: "10/11/2023"
output: html_document
---

# Overview
Summary product for MAS: acres treated per year by region by veg type. Forest/woodland/shrub/grass

One table, columns = region, priority, treatment intensity (500k, 1m, 2.3 mil), and Years (1-5, 6-10, 11-15, 16-20; equivalent to percentile group)



# Library
```{r}
library(tidyverse)
library(sf)
library(vroom)
library(tidyr)
```


# Data

## List of csv files
```{r}
listRuns <- list.files(path="../data/RunIDVeg",pattern='csv$', full.names = TRUE)
```

```{r}
listRuns
```



### Name items in a list with file name
```{r}
names(listRuns) <- tools::file_path_sans_ext(basename(listRuns))
```

```{r}
listRuns
```
# Functions
```{r}
geousa <- function(list){
  purrr::map(list, read.csv) %>%
    map2(names(.), ~mutate(.x, Tx = .y)) %>%
  bind_rows() %>%
    separate(., Tx, into = c("VegClass", "RunId", "RRK", "Priority", "TxIntense", "dateProc"), sep = '_', convert=TRUE, extra='merge') %>%
    group_by(tx_type, VegClass, RRK, Priority, TxIntense) %>%
     summarize(TxSqM = sum(sum)) %>%
    mutate(vegType = ifelse(VegClass == "Class1", "Herb",
                                     ifelse(VegClass == "Class2", "Shrub",
                                            ifelse(VegClass == "Class3", "Hardwood",
                                                   ifelse(VegClass == "Class4", "Softwood", "F"))))) %>%
    mutate(TxAcres = TxSqM/4047) %>%
    dplyr::select(RRK, Priority, TxIntense, tx_type, VegClass, vegType, TxSqM, TxAcres)
}

```

```{r}
combine <- function(list){
  purrr::map(list, read.csv) %>%
    map2(names(.), ~mutate(.x, Tx = .y)) %>%
  bind_rows() %>%
    separate(., Tx, into = c("VegClass", "RunId", "RRK", "Priority", "TxIntense", "dateProc"), sep = '_', convert=TRUE, extra='merge')
}
```
    mutate(totTxSqkm = ifelse(VT == "Herb", 10203,
                                     ifelse(VT == "Shrub", 26841,
                                            ifelse(VT == "Hardwood", 11996,
                                                   ifelse(VT == "Softwood", 44567, "F"))))) %>%
    mutate(totTxSqkm = as.numeric(totTxSqkm)) %>%
    mutate(totTxSqM = totTxSqkm*1000000) %>%
    mutate(prctTx = (TxSqM/totTxSqM)*100)
    
    
For Herb (1), Shrub (2), Hardwood (3), softwood (4)

```{r}
( run = geousa(listRuns) )
```

```{r}

(huc_runs = combine(listRuns))
```




# Write Summary Table
```{r}
write.csv(run, "../outputs/SummarizeMasFcatRuns.csv", row.names = F)
```