---
title: "Summary TX run Hucs"
author: "Anna Talucci"
date: "10/22/2023"
output: html_document
---


# Overview
Summary product for MAS: acres treated per year by region by veg type. Forest/woodland/shrub/grass

One table, columns = region, priority, treatment intensity (500k, 1m, 2.3 mil), and Years (1-5, 6-10, 11-15, 16-20; equivalent to percentile group)

# Global options
prevent scientific notation; use =0 to reset
```{r}
options(scipen=999)
```

# Library
```{r}
library(tidyverse)
library(sf)
library(vroom)
library(tidyr)
```


# Data

## List of csv files

```{r}
listRuns <- list.files(path="../data/HUCRunIdVeg",pattern='csv$', full.names = TRUE)
```

```{r}
listRuns
```



### Name items in a list with file name
```{r}
names(listRuns) <- tools::file_path_sans_ext(basename(listRuns))
```

```{r}
listRuns
```
# Functions
For Herb (1), Shrub (2), Hardwood (3), softwood (4)
```{r}
geousa <- function(list){
  purrr::map(list, read.csv) %>%
    map2(names(.), ~mutate(.x, Tx = .y)) %>%
  bind_rows() %>%
    separate(., Tx, into = c("VegClass", "Run"), sep = '_', convert=TRUE, extra='merge') %>%
    group_by(tx_type, VegClass, RRK, Priority, TxIntense, RunId, huc12) %>%
     summarize(TxSqM = sum(sum)) %>%
    mutate(vegType = ifelse(VegClass == "Class1", "Herb",
                                     ifelse(VegClass == "Class2", "Shrub",
                                            ifelse(VegClass == "Class3", "Hardwood",
                                                   ifelse(VegClass == "Class4", "Softwood", "F"))))) %>%
    mutate(TxAcres = round(TxSqM/4047, 1)) %>%
    dplyr::select(RRK, Priority, TxIntense, huc12, RunId, tx_type, VegClass, vegType, TxSqM, TxAcres)
}

```

# Apply function to list
```{r}
( run = geousa(listRuns) )
```

# Check data

```{r}
( new_DF <- run[rowSums(is.na(run)) > 0,] )
```
```{r}
sum(new_DF$TxAcres)

```
```{r}
run %>% filter(RRK =="CC")
```

# Write Summary Table
```{r}
write.csv(run, "../outputs/SummarizeMasFcatHUCRuns.csv", row.names = F)
```