---
title: "Treatment Math"
author: "Anna Talucci"
date: "6/3/2023"
output: html_document
---


# Packages
```{r}
library(tidyverse)
library(sf)
```

# Data
## Tx area
```{r}
sn = read.csv("../data/TxArea/snHucTreat10WuiBpPrctRk_2023-06-04.csv")
nc = read.csv("../data/TxArea/ncHucTreat10WuiBpPrctRk_2023-06-04.csv")
cc = read.csv("../data/TxArea/ccHucTreat10WuiBpPrctRk_2023-06-04.csv")
sc = read.csv("../data/TxArea/scHucTreat10WuiBpPrctRk_2023-06-04.csv")
```

## Hucs
```{r}
huc = st_read("../data/TxHucs/allHucsPrctRankWIP.shp", "allHucsPrctRankWIP")
```

# Bind csv
```{r}
( txarea = bind_rows(cc, nc, sc, sn) %>%
    dplyr::select(huc12, TxArea))
```
# Join TxArea to Hucs
```{r}
( hucTxArea = merge(x = huc, y = txarea, by = "huc12", all = TRUE) )
```

# Plot
```{r}
ggplot(huc, aes(group="RRK_Region")) +
  geom_sf(aes(color = RRK_Region)) 
```

```{r}
huc
```
2878 Hucs across 4 RRK regions
```{r}
huc1 = huc[is.na(huc$RRK_Region),]
```
```{r}
huc1
```
41 HUCs with NAs
```{r eval=FALSE, include=FALSE}
st_write(huc1, "../outputs/HUCsWithNa41.shp", driver="ESRI Shapefile")
```
```{r}
huc2 = huc %>% st_drop_geometry()
  huc2[is.na(huc2$RRK_Region),]
```

# Total Hucs per RRK
```{r}
huc %>% group_by(RRK_Region) %>% 
  summarise(n = n())
```




# Add Percentile group
## WUI

### Sierra Nevada WUI

```{r}
hucTxArea %>% 
    filter(RRK_Region=="Sierra Nevada Region")
```

```{r}
( snWui25 = hucTxArea %>% 
    filter(RRK_Region=="Sierra Nevada Region") %>%
    filter(WuiPrct <=25) %>%
    mutate(TxWuiPrctl=25) %>%
    mutate(TxHucNos=287)
  )
```
(x>=3&x<=7)
```{r}
( snWui50 = hucTxArea %>% 
    filter(RRK_Region=="Sierra Nevada Region") %>%
    filter(WuiPrct >25& WuiPrct <=50) %>%
    mutate(TxWuiPrctl=50) %>%
    mutate(TxHucNos=287)
  )
```

```{r}
( snWui75 = hucTxArea %>% 
    filter(RRK_Region=="Sierra Nevada Region") %>%
    filter(WuiPrct >50& WuiPrct <=75) %>%
    mutate(TxWuiPrctl=75) %>%
    mutate(TxHucNos=287)
  )
```

```{r}
( snWui100 = hucTxArea %>% 
    filter(RRK_Region=="Sierra Nevada Region") %>%
    filter(WuiPrct >75) %>%
    mutate(TxWuiPrctl=100) %>%
    mutate(TxHucNos=287)
   )
```

### North Coast WUI
```{r}
hucTxArea %>% 
    filter(RRK_Region=="North Coast Region")
```

```{r}
( ncWui25 = hucTxArea %>% 
    filter(RRK_Region=="North Coast Region") %>%
    filter(WuiPrct <=25) %>%
    mutate(TxWuiPrctl=25) %>%
    mutate(TxHucNos=193)
  )
```
(x>=3&x<=7)
```{r}
( ncWui50 = hucTxArea %>% 
    filter(RRK_Region=="North Coast Region") %>%
    filter(WuiPrct >25& WuiPrct <=50) %>%
    mutate(TxWuiPrctl=50) %>%
    mutate(TxHucNos=194)
  )
```

```{r}
( ncWui75 = hucTxArea %>% 
    filter(RRK_Region=="North Coast Region") %>%
    filter(WuiPrct >50& WuiPrct <=75) %>%
    mutate(TxWuiPrctl=75) %>%
    mutate(TxHucNos=193)
  )
```

```{r}
( ncWui100 = hucTxArea %>% 
    filter(RRK_Region=="North Coast Region") %>%
    filter(WuiPrct >75) %>%
    mutate(TxWuiPrctl=100) %>%
    mutate(TxHucNos=194)
  )
```

## Central Coast WUI
```{r}
hucTxArea %>% 
    filter(RRK_Region=="Central Coast Region")
```

```{r}
( ccWui25 = hucTxArea %>% 
    filter(RRK_Region=="Central Coast Region") %>%
    filter(WuiPrct <=25) %>%
    mutate(TxWuiPrctl=25) %>%
    mutate(TxHucNos=108)
  )
```
(x>=3&x<=7)
```{r}
( ccWui50 = hucTxArea %>% 
    filter(RRK_Region=="Central Coast Region") %>%
    filter(WuiPrct >25& WuiPrct <=50) %>%
    mutate(TxWuiPrctl=50) %>%
    mutate(TxHucNos=109)
  )
```

```{r}
( ccWui75 = hucTxArea %>% 
    filter(RRK_Region=="Central Coast Region") %>%
    filter(WuiPrct >50& WuiPrct <=75) %>%
    mutate(TxWuiPrctl=75) %>%
    mutate(TxHucNos=109)
  )
```

```{r}
( ccWui100 = hucTxArea %>% 
    filter(RRK_Region=="Central Coast Region") %>%
    filter(WuiPrct >75) %>%
    mutate(TxWuiPrctl=100) %>%
    mutate(TxHucNos=109)
  )
```

## South Coast WUI
```{r}
hucTxArea %>% 
    filter(RRK_Region=="South Coast Region")
```

```{r}
( scWui25 = hucTxArea %>% 
    filter(RRK_Region=="South Coast Region") %>%
    filter(WuiPrct <=25)%>%
    mutate(TxWuiPrctl=25) %>%
    mutate(TxHucNos=120)
  )
```
(x>=3&x<=7)
```{r}
( scWui50 = hucTxArea %>% 
    filter(RRK_Region=="South Coast Region") %>%
    filter(WuiPrct >25& WuiPrct <=50) %>%
    mutate(TxWuiPrctl=50) %>%
    mutate(TxHucNos=120)
  )
```

```{r}
( scWui75 = hucTxArea %>% 
    filter(RRK_Region=="South Coast Region") %>%
    filter(WuiPrct >50& WuiPrct <=75) %>%
    mutate(TxWuiPrctl=75) %>%
    mutate(TxHucNos=120)
  )
```

```{r}
( scWui100 = hucTxArea %>% 
    filter(RRK_Region=="South Coast Region") %>%
    filter(WuiPrct >75) %>%
    mutate(TxWuiPrctl=100) %>%
    mutate(TxHucNos=120)
  )
```
## Recombine HUCs with added attributes

### Within RRK
```{r}
( snWuiTx = bind_rows(snWui25, snWui50, snWui75, snWui100) )
```

```{r}
( ncWuiTx = bind_rows(ncWui25, ncWui50, ncWui75, ncWui100) )
```

```{r}
( ccWuiTx = bind_rows(ccWui25, ccWui50, ccWui75, ccWui100) )
```

```{r}
( scWuiTx = bind_rows(scWui25, scWui50, scWui75, scWui100) )
```

### All RRKs
```{r}
( allWuiTx = bind_rows(snWuiTx, ncWuiTx, ccWuiTx, scWuiTx) )
```

# BP
## Sierra Nevada BP


```{r}
( snBp25 = snWuiTx %>% 
    filter(BpPrct <=25) %>%
    mutate(TxBpPrctl=25) 
  )
```
(x>=3&x<=7)
```{r}
( snBp50 = snWuiTx %>% 
    filter(BpPrct >25& BpPrct <=50) %>%
    mutate(TxBpPrctl=50) 
  )
```

```{r}
( snBp75 = snWuiTx %>% 
    filter(BpPrct >50& BpPrct <=75)  %>%
    mutate(TxBpPrctl=75) 
  ) 

    
```

```{r}
( snBp100 = snWuiTx %>% 
    filter(BpPrct >75)   %>%
    mutate(TxBpPrctl=100) 
  ) 
    
```

## North Coast BP


```{r}
( ncBp25 = ncWuiTx %>% 
    filter(BpPrct <=25)  %>%
    mutate(TxBpPrctl=25) 
  ) 
    
```
(x>=3&x<=7)
```{r}
( ncBp50 = ncWuiTx %>% 
    filter(BpPrct >25& BpPrct <=50) %>%
    mutate(TxBpPrctl=50) 
  ) 
    
```

```{r}
( ncBp75 = ncWuiTx %>% 
    filter(BpPrct >50& BpPrct <=75) %>%
    mutate(TxBpPrctl=75) 
  ) 
    
```

```{r}
( ncBp100 = ncWuiTx %>% 
    filter(BpPrct >75)  %>%
    mutate(TxBpPrctl=100) 
  ) 
    
```

## Central Coast BP
```{r}
hucTxArea %>% 
    filter(RRK_Region=="Central Coast Region")
```

```{r}
( ccBp25 = ccWuiTx %>% 
    filter(BpPrct <=25) %>%
    mutate(TxBpPrctl=25) 
  ) 
```
(x>=3&x<=7)
```{r}
( ccBp50 = ccWuiTx %>% 
    filter(BpPrct >25& BpPrct <=50) %>%
    mutate(TxBpPrctl=50) 
  ) 
```

```{r}
( ccBp75 = ccWuiTx %>% 
    filter(BpPrct >50& BpPrct <=75)  %>%
    mutate(TxBpPrctl=75) 
  ) 
    
```

```{r}
( ccBp100 = ccWuiTx %>% 
    filter(BpPrct >75)  %>%
    mutate(TxBpPrctl=100) 
  ) 
```

## South Coast BP
```{r}
hucTxArea %>% 
    filter(RRK_Region=="South Coast Region")
```

```{r}
( scBp25 = scWuiTx %>% 
        filter(BpPrct <=25) %>%
    mutate(TxBpPrctl=25) 
  ) 

```
(x>=3&x<=7)
```{r}
( scBp50 = scWuiTx %>% 
       filter(BpPrct >25& BpPrct <=50) %>%
    mutate(TxBpPrctl=50) 
  ) 
```

```{r}
( scBp75 = scWuiTx %>% 
       filter(BpPrct >50& BpPrct <=75) %>%
    mutate(TxBpPrctl=75) 
  ) 
```

```{r}
( scBp100 = scWuiTx %>% 
       filter(BpPrct >75)  %>%
    mutate(TxBpPrctl=75) 
  ) 
```
# Recombine HUCs with added attributes

## Within RRK
```{r}
( snBpTx = bind_rows(snBp25, snBp50, snBp75, snBp100) )
```

```{r}
( ncBpTx = bind_rows(ncBp25, ncBp50, ncBp75, ncBp100) )
```

```{r}
( ccBpTx = bind_rows(ccBp25, ccBp50, ccBp75, ccBp100) )
```

```{r}
( scBpTx = bind_rows(scBp25, scBp50, scBp75, scBp100) )
```

## All RRKs
```{r}
( allDataTx = bind_rows(snBpTx, ncBpTx, ccBpTx, scBpTx) )
```

```{r}
(
  allDataTx1 = allDataTx %>% 
    mutate(TxSizeSqm = 404686) %>%
    mutate(TxSizeAc = 100) %>%
    mutate(TxRadiiM = (sqrt(TxSizeSqm))/2) %>%
    dplyr::select(huc12:TxBpPrctl,TxArea, TxSizeSqm, TxSizeAc,TxRadiiM,  geometry)
)
```
# Write to shapefile
```{r}
st_write(allDataTx1, "../outputs/hucsShp/TxPrctRankRrkWip.shp", driver="ESRI Shapefile")
```