---
title: "Weather Select and Org for Gridfire"
author: "Anna Talucci"
date: "5/16/2024"
output: html_document
---


```{r clearEnvironment, include=FALSE}
rm(list=ls())
```

```{r globalOptions, include=FALSE}
options(scipen=999) #Prevent scientific notation of numeric values; use =0 to reset
```

# Overview
Generate json file for for select HUC for each time step. 

Filter weather data extracted from EE. Join weather data to Hucs. 

Required Naming convention for GridFire 
temperature
relative-humidity
wind-speed-20ft
wind-from-direction
foliar-moisture
fuel-moisture
dead
1hr
10hr
100hr
live
herbaceous
woody
# Packages
```{r}
library('tidyverse')
library('jsonlite')
```


# Data
```{r}
percentiles1524 =read.csv(file = "../data/weather/percentile/weatherSN_2015_2024.csv", header = TRUE)
percentiles2534 =read.csv(file = "../data/weather/percentile/weatherSN_2025_2034.csv", header = TRUE)
percentiles3544 =read.csv(file = "../data/weather/percentile/weatherSN_2035_2044.csv", header = TRUE)
```


# Filter 98th percentile per time step per variable

## Temperature
```{r}
( perct98regionTemp1524 = percentiles1524 %>% 
    group_by(huc12) %>% 
  filter(tempPCT %in% c(98:100)) %>%
    arrange(desc(temperature))
    
              
)
```

```{r}
( perct98regionTemp2534 = percentiles2534 %>% 
  filter(tempPCT %in% c(98:100)) %>%
    ungroup()%>%
    summarize(temp_mean = mean(temperature),
              temp_min = min(temperature),
              temp_max = max(temperature),
              rh_mean = mean(relative.humidity), 
              rh_min = min(relative.humidity), 
              rh_max = max(relative.humidity), 
              ws_mean = mean(wind.speed.20ft),
              ws_min = min(wind.speed.20ft),
              ws_max = max(wind.speed.20ft),
              n = n()/1148) %>%
    mutate(sample = "98th percentile Temp", 
           region = "sn",
           years = "2025-2034")
              
)
```

```{r}
( perct98regionTemp3544 = percentiles3544 %>% 
  filter(tempPCT %in% c(98:100)) %>%
    ungroup()%>%
    summarize(temp_mean = mean(temperature),
              temp_min = min(temperature),
              temp_max = max(temperature),
              rh_mean = mean(relative.humidity), 
              rh_min = min(relative.humidity), 
              rh_max = max(relative.humidity), 
              ws_mean = mean(wind.speed.20ft),
              ws_min = min(wind.speed.20ft),
              ws_max = max(wind.speed.20ft),
              n = n()/1148) %>%
    mutate(sample = "98th percentile Temp", 
           region = "sn",
           years = "2035-2044")
              
)
```


# Function for rename and final column selection
```{r}
orgDf2 <- function(x){
  x %>% mutate(foliar.moisture=82.2) %>%
  dplyr::select(-RRK_Rgn, -model, -scenario) %>%
    rename('relative-humidity'=relative.humidity, 'wind-from-direction'=wind.from.direction, 'wind-speed-20ft'=wind.speed.20ft, 'foliar-moisture'=foliar.moisture) %>%
    arrange(date)
    
}

```


```{r}
( df2 = rh_top1 %>% 
  full_join(., temp_top1, by = c("huc12", "rowId")) %>% 
  full_join(., wind_top1, by = c("huc12", "rowId")) %>%
  select(-rowId)
)
```

# Json Function
```{r}
jsonFun <- function(x) {
  huc12 = unique(x$huc12);
x %>% arrange(date) %>%
    ungroup() %>%
  dplyr::select(-huc12, -date) %>%
  jsonlite::toJSON(pretty = TRUE, auto_unbox = TRUE) %>%
  write(., paste("../outputs/WeatherJsonHuc/WeatherJsonHucSelect/",huc12,'_2039.json'))
  
}
```

```{r}
dflist = df2 %>% group_split(huc12) %>% set_names(df2$huc12 %>% unique %>% sort)
```

```{r}
dflist %>% map_dfr(~ .x %>% jsonFun())
```
