---
title: "Weather for Hucs"
author: "Anna Talucci"
date: "11/18/2023"
output: html_document
---



# Overview
Generate json file for for each HUC for each time step with top 200 temperature days per time step.
Filter weather data extracted from EE. Join weather data to Hucs. Convert from .shp to .json.

Select daily weather based on 200 highest temperature days.

SC test huc huc12==180701060203

Name variables
temperature
relative-humidity
wind-speed-20ft
wind-from-direction
foliar-moisture
fuel-moisture
dead
1hr
10hr
100hr
live
herbaceous
woody


HUCs per region

Central Coast Region [435], 
North Coast Region [774], 
Sierra Nevada Region [1148], 
South Coast Region [480]

# Global options
prevent scientific notation; use =0 to reset
```{r}
options(scipen=999)
```

# Packages
```{r}
library('tidyverse')

library('jsonlite')

```

# Data
## CSV weather data
output from GEE
```{r}
list <- list.files(path="../data/weather/timestep2534/cc", pattern='csv$', full.names = TRUE)
```

```{r}
list
```
# Function to combine CSV
## Combine, Clean, and organize
```{r}
combineCsv <- function(list){
  purrr::map(list, read.csv) %>%
  bind_rows() %>%
    dplyr::select(-system.index, -.geo) 
}
```

```{r}
orgDf <- function(x) {
  x %>%
    pivot_longer(cols = starts_with("GF"),
    names_to = "variable",
    values_to = "value", 
    values_drop_na = TRUE) %>%
    separate(col=variable, into=c("model","scenario","date", "climate"), sep="_", fill="right")  %>%
    pivot_wider(names_from = climate, values_from = value) %>%
    mutate(tasmax = ((tasmax-273.15)*9/5+32)) %>%
    rename(temperature=tasmax, relative.humidity=rhsmin, wind.speed.20ft=ws, wind.from.direction=wd) 
}
```

```{r}
temp <- function(x){
  x %>% 
    group_by(huc12) %>%
    arrange(desc(temperature)) %>%
    top_n(n=200)
}
```

```{r}
orgDf2 <- function(x){
  x %>% mutate(foliar.moisture=82.2) %>%
  dplyr::select(-RRK_Rgn, -model, -scenario) %>%
    rename('relative-humidity'=relative.humidity, 'wind-from-direction'=wind.from.direction, 'wind-speed-20ft'=wind.speed.20ft, 'foliar-moisture'=foliar.moisture) %>%
    arrange(date)
    
}

```

## Apply  functions

```{r}
list %>% combineCsv() %>% orgDf() # for sample size
```

```{r}
df = list %>% combineCsv() %>% orgDf() %>% temp() %>% orgDf2() 
```

```{r}
df
```

```{r}
dflist = df %>% group_split(huc12) %>% set_names(df$huc12 %>% unique %>% sort)
```

```{r}
df1 = dflist[[1]]
```

```{r}
jsonFun <- function(x) {
  huc12 = unique(x$huc12);
x %>% arrange(date) %>%
    ungroup() %>%
  dplyr::select(-huc12, -date) %>%
  jsonlite::toJSON(pretty = TRUE, auto_unbox = TRUE) %>%
  write(., paste("../outputs/WeatherJsonHuc/ts2034CC/",huc12,'_2034.json'))
  
}
```

```{r}
dflist %>% map_dfr(~ .x %>% jsonFun())
```
**NOTES:**

*Missing HUC due to centroid placement over water*
* For SC Use values from 180701070002 for Huc 180701070003
* For cc use values from 180600020804 for Huc 180600150305


**THE END**