---
title: "Weather for Hucs Extreme"
author: "Anna Talucci"
date: "5/9/2024"
output: html_document
---

```{r clearEnvironment, include=FALSE}
rm(list=ls())
```

```{r globalOptions, include=FALSE}
options(scipen=999) #Prevent scientific notation of numeric values; use =0 to reset
```

# Overview
Updated from WeatherForHucs.Rmd

This script combines cvs and adds percentiles.
Generate json file for for each HUC for each time step with top 200 temperature days per time step.
Filter weather data extracted from EE. Join weather data to Hucs. 

Select daily weather based on 200 highest temperature days.

SC test huc huc12==180701060203

Name variables
temperature
relative-humidity
wind-speed-20ft
wind-from-direction
foliar-moisture
fuel-moisture
dead
1hr
10hr
100hr
live
herbaceous
woody


HUCs per region

Central Coast Region [435], 
North Coast Region [774], 
Sierra Nevada Region [1148], 
South Coast Region [480]

**UPDATES**
2024 May 1 -> issue fix for converting wind speed from m/s to mph
2024 May 1 -> issue fix for weighting top 200 temperatures for temp, old code was missing weighting factor resulting in larger spread.
2024 May 9 -> weighting and 98th percentile

**SPECIAL NOTES**
*Missing HUC due to centroid placement over water*
* For SC Use values from 180701070002 for Huc 180701070003
* For cc use values from 180600020804 for Huc 180600150305

# Packages
```{r}
library('tidyverse')
library('jsonlite')
```

# Data
## CSV weather data
output from GEE
```{r}
list <- list.files(path="../data/EE_WeatherData/timestep1524/sn", pattern='csv$', full.names = TRUE)
```

```{r}
list
```

# Function to combine CSV
## Combine, Clean, and organize
```{r}
combineCsv <- function(list){
  purrr::map(list, read.csv) %>%
  bind_rows() %>%
    dplyr::select(-system.index, -.geo) 
}
```

```{r}
orgDf <- function(x) {
  x %>%
    pivot_longer(cols = starts_with("GF"),
    names_to = "variable",
    values_to = "value", 
    values_drop_na = TRUE) %>%
    separate(col=variable, into=c("model","scenario","date", "climate"), sep="_", fill="right")  %>%
    pivot_wider(names_from = climate, values_from = value) %>%
    mutate(tasmax = ((tasmax-273.15)*9/5+32)) %>%
    mutate(ws = (ws*2.237)/1.15) %>% # m/s to mph; 10-m to 20ft
    rename(temperature=tasmax, relative.humidity=rhsmin, wind.speed.20ft=ws, wind.from.direction=wd) 
}
```

```{r}
temp <- function(x){
  x %>% 
    group_by(huc12) %>%
    arrange(desc(temperature)) %>%
    top_n(n=200, wt=temperature) 
}
```

```{r}
orgDf2 <- function(x){
  x %>% mutate(foliar.moisture=82.2) %>%
  dplyr::select(-RRK_Rgn, -model, -scenario) %>%
    rename('relative-humidity'=relative.humidity, 'wind-from-direction'=wind.from.direction, 'wind-speed-20ft'=wind.speed.20ft, 'foliar-moisture'=foliar.moisture) %>%
    arrange(date)
    
}

```

## Apply  functions

```{r eval=FALSE, include=FALSE}
list %>% combineCsv() %>% orgDf() %>% group_by(huc12) %>% summarize(n=n()) # for sample size 
```
```{r eval=FALSE, include=FALSE}
list %>% combineCsv() %>% orgDf() 
```



```{r}
df = list %>% combineCsv() %>% orgDf() #%>% temp() %>% orgDf2() 
```

```{r}
df
```

```{r}
df %>%
  mutate(tempPCT = ntile(temperature, 100),
         rhPCT = ntile(-relative.humidity, 100),
         wsPCT = ntile(wind.speed.20ft, 100)) %>% 
  arrange(desc(wsPCT))
```

```{r}
dflist = df %>% group_split(huc12) %>% set_names(df$huc12 %>% unique %>% sort)
```

```{r}
df1 = dflist[[1]]
```

```{r}
jsonFun <- function(x) {
  huc12 = unique(x$huc12);
x %>% arrange(date) %>%
    ungroup() %>%
  dplyr::select(-huc12, -date) %>%
  jsonlite::toJSON(pretty = TRUE, auto_unbox = TRUE) %>%
  write(., paste("../outputs/WeatherJsonHuc/ts2034CC/",huc12,'_2034.json'))
  
}
```

```{r}
dflist %>% map_dfr(~ .x %>% jsonFun())
```




**THE END**