---
title: "WUI 500 RUNID Veg"
author: "Anna Talucci"
date: "11/6/2023"
output: html_document
---

---
title: "Summarize Treatment Runs"
author: "Anna Talucci"
date: "10/11/2023"
output: html_document
---

# Overview
Summary product for MAS: acres treated per year by region by veg type. Forest/woodland/shrub/grass

One table, columns = region, priority, treatment intensity (500k, 1m, 2.3 mil), and Years (1-5, 6-10, 11-15, 16-20; equivalent to percentile group)



# Library
```{r}
library(tidyverse)
library(sf)
library(vroom)
library(tidyr)
```


# Data

## List of csv files
```{r}
wlistRuns <- list.files(path="../data/RunIdVegWui500",pattern='csv$', full.names = TRUE)
```

```{r}
wlistRuns
```



### Name items in a list with file name
```{r}
names(wlistRuns) <- tools::file_path_sans_ext(basename(wlistRuns))
```

```{r}
wlistRuns
```
# Functions
```{r}
wpart1 <- function(list){
  purrr::map(list, read.csv) %>%
    map2(names(.), ~mutate(.x, Tx = .y)) %>%
  bind_rows() %>%
    separate(., Tx, into = c("VegClass", "RunId", "RRK", "Priority", "TxIntense", "dateProc"), sep = '_', convert=TRUE, extra='merge') %>%
    mutate(vegType = ifelse(VegClass == "Class1", "Herb",
                                     ifelse(VegClass == "Class2", "Shrub",
                                            ifelse(VegClass == "Class3", "Hardwood",
                                                   ifelse(VegClass == "Class4", "Softwood", "F")))))  
}
```

%>%

    group_by(RRK, Priority, TxIntense,VegClass, vegType, tx_code, tx_type) %>%
     summarize(TxSqM = sum(sum)) %>%
        mutate(TxAcres = TxSqM/4047) %>%
    dplyr::select(RRK, Priority, TxIntense, tx_type, tx_code, VegClass, vegType, TxSqM, TxAcres)



```{r}
( wrun_part1 = wpart1(wlistRuns) )
```
```{r}
unique(wrun_part1$tx_type)
```

```{r}
(t1 = wrun_part1 %>% filter(tx_type== "year_int_16-20") )
unique(t1$RunId)
```

```{r}
( t2 = wrun_part1 %>% filter(tx_type== "year_int_1-5") )
unique(t2$RunId)
```

```{r}
unique(wuicheck$tx_type)
```
```{r}
( biggroupsum = run_part1 %>% 
    group_by(Priority, TxIntense, tx_type) %>%
     summarize(TotAcres = sum(TxAcres)) )
```


```{r}
unique(run_part1$tx_type)
```

```{r}

(huc_runs = combine(listRuns))
```



